Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-19 doc/GMP2015/appendix_a.tex
Updated Section 7 based on new Section 3

First notice that since $C_i \cup C_j$ is well-constrained, by Lemma~\ref{lem:pinned_union_intersection},
both $C_i$ and $C_j$ are connected well-constrained vertex-maximal proper subgraphs of  $C$.
Since $C_j \cup C_j = C$, there are no edges in $C$ that is not contained in a well-constrained subgraph, so $C$ does not have any single-edge child node, and $C_k$ is a connected well-constrained vertex-maximal proper subgraph of  $C$.

>>>>

First notice that since $C_i \cup C_j$ is well-constrained, by Observation~\ref{lem:pinned_union_intersection},
both $C_i$ and $C_j$ are connected well-constrained vertex-maximal proper subgraphs of  $C$.
Since $C_j \cup C_j = C$, there are no edges in $C$ that is not contained in a well-constrained subgraph, so $C$ does not have any single-edge child node, and $C_k$ is a connected well-constrained vertex-maximal proper subgraph of  $C$.

### 2014-12-19 doc/GMP2015/s08_pinnedline.tex
Updated Section 7 based on new Section 3

The optimal DR-plan of Section \ref{sec:DRP} can also be applied to analyze and solve
the structure of  cross-linking collagen and cellulose microfibrils 
in animal and plant cell walls, and actin filaments in the cytoskeleton
by modeling these structures as \dfn{pinned line-incidence
systems}.

@@

Figure~\ref{fig:pinned_line} shows an example of a pinned line-incidence graph,
where the grey ovals denote pins representing attachments of fibrils,
and the vertices $a_1,a_2,\ldots, c_3$ represent cross-linkings.
% and the black dots stand for vertices/cross-linkings.
%There are  and 10 vertices/cross-linkings in the graph.
The graph is well-constrained, with 12 vertices and 24 edges/pins.

\begin{figure}
  \centering
   \includegraphics[width=.8\linewidth]{img/pinned}
\caption{ A well-constrained pinned line-incidence graph.}
\label{fig:pinned_line}
\end{figure}

@@

In this section, we will adapt the results in Section~\ref{sec:DRP}
to give the Optimal DR-plan for pinned line-incidence graphs.
First, we note that %unlike bar-joint graphs,
\vemph{a well-constrained pinned line-incidence graph can be disconnected},
being the disjoint union of two or more well-constrained subgraphs.
This is because the pins have fixed positions on the plane.
%
%the following difference of pinned line-incidence graphs from the bar-joint graphs.
%
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs.
%
%\begin{itemize}
%
%\item For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%no trivial motion exists, therefore {\em no trivial over-constrained graphs exist} (the smallest over-constrained graph has $6$ vertices).\\
%In particular, note that both a single vertex and a single edge are under-constrained graphs.
%
%\item
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs. \\
%%Without loss of generality,
%%we slightly modify the requirement of DR-plan for pinned line-incidence graphs
%%such that only connected subgraphs can be considered as a node of the DR-plan.
%
%\end{itemize}
%
We define a \dfn{trivial} graph to be a single vertex and make the following modification to the definition of the DR-plan:

@@

\begin{definition}
The \dfn{DR-plan} of a well-constrained pinned line-incidence graph $G$ is one in which
(1) each child node of a non-leaf node $C$ is either an edge not contained in any well-constrained proper subgraph of $C$, or a \dfn{connected} well-constrained vertex-maximal proper subgraph of $C$, and
(2) a leaf node is a single edge.
% Definition~\ref{def:drp} with  modified rules number 2 and 4:
%    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line-incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
%    \begin{enumerate}
%        %\item The root of the tree `contains' $G$.
%        \item[2] For any non-leaf node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$.
%        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
%        \item[4] A node containing a single edge is a leaf.
%    \end{enumerate}
\end{definition}

With the above modification, we now adapt Theorem~\ref{theorem:main}
for the optimal DR-plan for pinned line-incidence graphs.

\begin{corollary}\label{cor:pinned}
Given a well-constrained pinned line-incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$.
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
\end{corollary}

The following lemma serves a similar function to Remark~\ref{lemma:union_intersection} in Section~\ref{sec:union_intersection}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
and can be proved using a similar counting based argument.

\begin{lemma}\label{lem:pinned_union_intersection}
Let $F_i$ and $F_j$ to be subgraphs of the same well-constrained graph $F$,
where each of them can be either a single edge or a connected well-constrained subgraph.
There are only two possible cases:
(1) At least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is under-constrained, if and only if $F_i \cap F_j$ is trivial; and (2) both $F_i$ and $F_j$ are well-constrained, if and only if $F_i \cup F_j$ is well-constrained, if and only if $F_i \cap F_j$ is well-constrained.
%The following table summarizes all bijections:
%\setlength{\tabcolsep}{3pt}
%{\small
%\begin{center}
%\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
%\hline
%\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
% \centering--- &  \sout{over-constrained}          &  \centering --- \tabularnewline \hline
%at least one of $F_i,F_j$ is an edge & under-constrained       &  \centering a vertex (under-constrained)  \tabularnewline \hline
%both $F_i$ and $F_j$ are well-constrained & well-constrained        &  \centering well-constrained  \tabularnewline \hline
% \centering --- & ---                     &  \centering \sout{under-constrained} \tabularnewline \hline
%\end{tabular}
%\end{center}
%}
%\setlength{\tabcolsep}{6pt}
\end{lemma}

Given Lemma~\ref{lem:pinned_union_intersection}, % and the modified definition of DR-plan,
proofs of Lemma~\ref{lemma:wc_intersection_is_C} and \ref{lemma:uc_intersection_makes_all_uc} straightforwardly extend to  pinned line-incidence graphs.
The proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for pinned
line-incidence graphs is given in Appendix~\ref{sec:appendix_pinned}.
%The following lemma serves as Lemma~ for pinned line-incidence and can be proved similarly.
%\begin{lemma}
%\label{lem:vertex_intersection}
%If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
%\end{lemma}

Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lemma:uc_intersection_makes_all_uc},
it is straightforward to adapt the proof of Theorem~\ref{theorem:main}
to  pinned line-incidence graphs,
thus proving Corollary~\ref{cor:pinned}.
Consequently, we can efficiently find the optimal DR-plan for  pinned line-incidence graphs using basically the same algorithm as for  bar-joint graphs.

\noindent
\note The recombination problem for  pinned line-incidence systems is trivial.
Since the pins are given fixed positions in the plane,
the solutions of a well-constrained sub-system will automatically be consistent with solutions of the remaining of the system.

>>>>

The canonical DR-plan of Section \ref{sec:DRP} can also be applied to analyze and solve
the structure of  cross-linking collagen and cellulose microfibrils 
in animal and plant cell walls, and actin filaments in the cytoskeleton
by modeling these structures as \dfn{pinned line-incidence systems}.

@@

Figure~\ref{fig:pinned_line} shows an example of a pinned line-incidence graph,
where the grey ovals denote pins representing attachments of fibrils,
and the vertices $a_1,a_2,\ldots, c_3$ represent cross-linkings.
% and the black dots stand for vertices/cross-linkings.
%There are  and 10 vertices/cross-linkings in the graph.
The graph is isostatic, with 12 vertices and 24 edges/pins.

\begin{figure}
  \centering
   \includegraphics[width=.7\linewidth]{img/pinned}
\caption{ An isostatic pinned line-incidence graph.}
\label{fig:pinned_line}
\end{figure}

@@

In this section, we will adapt the results in Section~\ref{sec:DRP}
to give the canonical DR-plan for pinned line-incidence graphs.
First, we note that %unlike bar-joint graphs,
\vemph{an isostatic pinned line-incidence graph can be disconnected},
being the disjoint union of two or more isostatic subgraphs.
This is because the pins have fixed positions on the plane.
%
%the following difference of pinned line-incidence graphs from the bar-joint graphs.
%
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs.
%
%\begin{itemize}
%
%\item For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%no trivial motion exists, therefore {\em no trivial over-constrained graphs exist} (the smallest over-constrained graph has $6$ vertices).\\
%In particular, note that both a single vertex and a single edge are under-constrained graphs.
%
%\item
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs. \\
%%Without loss of generality,
%%we slightly modify the requirement of DR-plan for pinned line-incidence graphs
%%such that only connected subgraphs can be considered as a node of the DR-plan.
%
%\end{itemize}
%
We define a \dfn{trivial} graph to be a single vertex and make the following modification to the definition of 
the canonical DR-plan:

@@

\begin{definition}
The \dfn{DR-plan} of a  pinned line-incidence graph $G$ is one in which
(1) each child node of a non-leaf node $C$ is either a \dfn{connected} rigid vertex-induced subgraph of $C$,
or an edge not contained in any  proper rigid subgraph of $C$, and (2) a leaf node is a single edge.
% Definition~\ref{def:drp} with  modified rules number 2 and 4:
%    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line-incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
%    \begin{enumerate}
%        %\item The root of the tree `contains' $G$.
%        \item[2] For any non-leaf node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$.
%        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
%        \item[4] A node containing a single edge is a leaf.
%    \end{enumerate}

The \dfn{canonical DR-plan} of $G$  is one in which 
the  children containing rigid subgraphs are connected isostatic vertex-maximal subgraphs of the parent.
\end{definition}

Theorem~\ref{theorem:canonical_is_optimal} and \ref{theorem:main}
hold for  pinned line-incidence graphs with the above modified definition. 
The proof is similar to the original proof (in the Appendix) using the same set of lemmas and  
%
%\begin{corollary}\label{cor:pinned}
%Given a isostatic pinned line-incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
%\begin{enumerate}
%    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$.
%    \item if $C_i \cap C_j$ is isostatic then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
%\end{enumerate}
%\end{corollary}
%
the following modified version of Observation~\ref{lemma:union_intersection},
% observation, which
%serves a similar function to Observation~\ref{lemma:union_intersection} in Section~\ref{sec:DRP}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
which  can be proved using a simple counting based argument.

\begin{observation}\label{lem:pinned_union_intersection}
Let $F_i$ and $F_j$ to be subgraphs of the same isostatic graph $F$,
where each of them can be either a single edge or a connected isostatic subgraph.
There are only two possible cases:
(1) At least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is under-constrained, if and only if $F_i \cap F_j$ is trivial; and (2) both $F_i$ and $F_j$ are isostatic, if and only if $F_i \cup F_j$ is isostatic, if and only if $F_i \cap F_j$ is isostatic.
%The following table summarizes all bijections:
%\setlength{\tabcolsep}{3pt}
%{\small
%\begin{center}
%\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
%\hline
%\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
% \centering--- &  \sout{over-constrained}          &  \centering --- \tabularnewline \hline
%at least one of $F_i,F_j$ is an edge & under-constrained       &  \centering a vertex (under-constrained)  \tabularnewline \hline
%both $F_i$ and $F_j$ are well-constrained & well-constrained        &  \centering well-constrained  \tabularnewline \hline
% \centering --- & ---                     &  \centering \sout{under-constrained} \tabularnewline \hline
%\end{tabular}
%\end{center}
%}
%\setlength{\tabcolsep}{6pt}
\end{observation}

Given Lemma~\ref{lem:pinned_union_intersection}, % and the modified definition of DR-plan,
Lemma~\ref{lemma:wc_intersection_is_C} and \ref{lemma:uc_intersection_makes_all_uc} straightforwardly extend to  pinned line-incidence graphs. The proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for pinned
line-incidence graphs is given in Appendix~\ref{sec:appendix_pinned}.
%The following lemma serves as Lemma~ for pinned line-incidence and can be proved similarly.
%\begin{lemma}
%\label{lem:vertex_intersection}
%If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
%\end{lemma}
%Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lemma:uc_intersection_makes_all_uc},
Thus it is straightforward to adapt the proof of Theorem~\ref{theorem:main}
to  pinned line-incidence graphs.
%thus proving Corollary~\ref{cor:pinned}.
%
Consequently, we can efficiently find the optimal DR-plan for  pinned line-incidence graphs using basically the same algorithm as for  bar-joint graphs.

\noindent
\note The recombination problem for  pinned line-incidence systems is trivial.
Since the pins are given fixed positions in the plane,
the solutions of a isostatic sub-system will automatically be consistent with solutions of the remaining of the system.
